Output Summary

### 2023-08-17 03-post-process/output-plots-children/03-fit-to-data.Rmd
Improve fit to data Rmd section

# Fit to Data {.tabset .tabset-pills}

## Figures {.tabset .tabset-dropdown}

@@

### Abundance Data {.tabset .tabset-pills}

#### Fall Parr Abundance

@@

#### Spring Smolt Abundance

@@

#### Adult Return Abundance

@@

### Survival Data {.tabset .tabset-dropdown}

#### Summer Parr $\rightarrow$ LGR

@@

#### Fall Parr $\rightarrow$ LGR

@@

#### Winter Parr $\rightarrow$ LGR

@@

#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

##### NOR

@@

##### HOR

@@

#### LGR Smolt $\rightarrow$ BON

@@

#### BON Adults $\rightarrow$ LGR

@@

### Composition Data {.tabset .tabset-pills}

@@

#### Weir Sampling {.tabset .tabset-dropdown}

@@

##### By Age/Origin {.tabset .tabset-pills}

@@

###### CAT

@@

###### LOS

@@

###### MIN

@@

###### UGR

@@

##### By Age {.tabset .tabset-pills}

@@

##### By Origin {.tabset .tabset-pills}

@@

##### Total Sample Size {.tabset .tabset-pills}

@@

#### Carcass Sampling {.tabset .tabset-dropdown}

@@

### Mean Length Data {.tabset .tabset-pills}

#### Summer Parr

@@

#### Spring Smolt

@@

```{r pp-check-output, child = "output-plots-children/03a-pp-checks.Rmd", eval = model_info$do_pp_check}
```

```{r waic-output, child = "output-plots-children/03b-waic.Rmd", eval = model_info$do_lppd}
```

>>>>

# Fit to Data {.tabset .tabset-dropdown}

@@

## Abundance Data {.tabset .tabset-dropdown}

### Fall Parr Abundance

@@

### Spring Smolt Abundance

@@

### Adult Return Abundance

@@

## Survival Data {.tabset .tabset-dropdown}

### Summer Parr $\rightarrow$ LGR

@@

### Fall Parr $\rightarrow$ LGR

@@

### Winter Parr $\rightarrow$ LGR

@@

### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

#### NOR {-}

@@

#### HOR {-}

@@

### LGR Smolt $\rightarrow$ BON

@@

### BON Adults $\rightarrow$ LGR

@@

## Composition Data {.tabset .tabset-pills}

@@

### Weir Sampling {.tabset .tabset-dropdown}

@@

#### By Age/Origin {.tabset .tabset-pills}

@@

##### CAT {-}

@@

##### LOS {-}

@@

##### MIN {-}

@@

##### UGR {-}

@@

#### By Age {.tabset .tabset-pills}

@@

#### By Origin {.tabset .tabset-pills}

@@

#### Total Sample Size {.tabset .tabset-pills}

@@

### Carcass Sampling {.tabset .tabset-dropdown}

@@

## Mean Length Data {.tabset .tabset-pills}

### Summer Parr

@@

### Spring Smolt

@@
